\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{apacite}
\usepackage[round, sort, numbers, authoryear, square]{natbib}

\title{Bubble shooter}

\author{
    Bavdaz, Luka\\
    \texttt{4228561}
    \and
    Clark, Liam\\
    \texttt{4303423}
    \and
    Gmelig Meyling, Jan-Willem\\
    \texttt{4305167}
    \and
    Hoek, Leon\\
    \texttt{4021606}
    \and
    Smulders, Sam\\
    \texttt{4225007}
}

\date{\today}

\begin{document}
\maketitle

% \begin{abstract}
% Your abstract.
% \end{abstract}

\pagenumbering{alph}

% ==========================================
% ASSIGNMENT 1
% 	REQUIREMENTS ANALYSIS
% ==========================================

\section{Requirements analysis}
The stakeholder wants a game like Frozen Bubble, with both the singleplayer and multiplayer modes. Frozen Bubble is a Bubble shooter game, in which players have to shoot colored bubbles with a bubble gun. The bubble gun can be aimed and then shoot a bubble of a specific color. When the shot bubble hits a group of bubbles (two or more) of the same colour, these bubbles will pop and the player will receive an amount of points. When the player fails to hit a bubble of the same colour multiple times, a new row of bubbles will be inserted at the top, pushing the other bubbles. When one of these bubbles reaches the bottom of the screen, or all bubbles are shot, the game is over, and the score will be saved into a highscore board.
\par In the single player mode, players will face various levels with a different layout of the bubbles.
\par In the multiplayer mode, each player has his own canvas with a bubble gun and the bubbles to shoot (split screen). The players have different key bindings to rotate and fire the bubble gun.


% ==========================================
% ASSIGNMENT 1
% 	FUNCTIONAL REQUIREMENTS
% ==========================================

\section{Functional requirements}
Each requirement is identified by a requirement identifier. This identifier consists of one or more marks pointing priority and status. For the priority status we use the \textit{MoSCoW Prioritisation} \citep{moscow} (\texttt{M} for must have, \texttt{S} for should have, \texttt{C} for could have, \texttt{W} for won't have) and a unique number. Requirements that require further concideration are marked with \texttt{TBD}.


\subsection{Must have}

\begin{itemize}
  \item \texttt{M-113} The player should be able to start a game through the menu

  \item When the player starts the game...
  \begin{enumerate}
    \item \texttt{M-114} The canvas is filled with bubbles of certain colours (for example: red, green and blue), the colours are distributed depending on the game mode
    \item \texttt{M-115} Bubbles in the canvas are snapped to the top of the canvas
  \end{enumerate}
  
  \item \texttt{M-116} The player should be able to aim the bubble cannon (\texttt{left} and \texttt{right}) using the mouse
  \item \texttt{M-117} The interface should show the colours for the upcomming bubbles to shoot

% ==========================================
%  BUBBLE SHOOT BEHAVIOUR
% ==========================================

  \item Behaviour for when a bubble is shot
  \begin{enumerate}
    \item \texttt{M-118} When a bubble hits a border of the canvas, it bounces
    \item \texttt{M-119} When a bubble hits another bubble, it snaps to it
    \item \texttt{M-120} When a bubble hits a group of bubbles of the same color, these bubbles should pop
    \item \texttt{M-121} When a bubble gets isolated from any bubble at the top of the canvas, they pop
    \item \texttt{M-122} When bubbles pop, points should be awarded to the player
    \item \texttt{M-123} When you do not succeed in popping bubbles, the player gets a penalty
    \item \texttt{M-124} For each a to be determined number of penalties a new row of bubbles with the remaining colours is inserted at the top, and other bubbles are shifted down
    \item \texttt{M-125} When a row of bubbles reaches the bottom of the canvas, the game is over
    \item \texttt{M-126} When all bubbles have popped, the game is finished
  \end{enumerate}
  
  \item There are two different modes to play:
  \begin{enumerate}
  
% ==========================================
% SINGLEPLAYER GAME REQUIREMENTS
% ==========================================
      \item \texttt{M-127} Singleplayer mode
      \begin{enumerate}
          \item \texttt{M-128} When a player finishes the game, a new level will appear
          \item \texttt{M-129} A new level is generated by distributing bubbles randomly within a grid
      \end{enumerate}

% ==========================================
% MULTIPLAYER GAME REQUIREMENTS
% ==========================================

      \item \texttt{M-140} Multiplayer mode
      \begin{enumerate}
          \item \texttt{M-141} In the multiplayer mode, each player has his own canvas with a bubble gun and the bubbles to shoot (split screen)
          \item \texttt{M-142} The players have different key bindings to rotate and fire the bubble gun
          \item \texttt{M-143} \textsc{Competitive multiplayer.} When a player shoots a bubble, a new bubble is inserted in the other players screen
          \item \texttt{M-144} In the multiplayer mode, the bubbles are distrubuted randomly
          \item \texttt{M-145} The player should be able to play against another player remotely using a network connection
      \end{enumerate}
      
      \item \texttt{M-146} The user should be able to switch between these modes through a menu
  \end{enumerate}
  
  
% ==========================================
% ASSIGNMENT 3
% M-160: POWER UP BUBBLES
% ==========================================
  \item \texttt{M-160} Every once in a while a player should get a power-up bubble loaded up in the cannon which has special abilities:
  
          \begin{enumerate}
          \item \texttt{M-161} A \textit{Joker Bubble} should pop with a bubble of any color. If it is adjacened to less than two bubbles, the joker receives the colour of the bubble it collided with
          \item \texttt{M-162} A \textit{Bomb Bubble} should pop all bubbles in a certain radius around it after colliding
          \item \texttt{M-163} A \textit{Stone Bubble} can't be popped directly but only by popping the bubbles that connect it to the top
          \item \texttt{M-164} A \textit{Drunk Bubble} should move in a more difficult to predict way, so the user will have more difficulty accurately aiming the bubble
		 
          \item \texttt{M-165} A \textit{Sound Bubble} makes a sound when shot, when moving, on impact or when popped
          \item \texttt{M-166} A \textit{Reversebomb Bubble} should add bubbles in all the empty spots in a certain radius around it after colliding
      \end{enumerate}
 
% ==========================================
% END M-160: POWER UP BUBBLES
% ==========================================
  
  
% ==========================================
% ASSIGNMENT 2
% M-170: Logging functionality
% ==========================================
  
  \item \texttt{M-170} The game should have logging functionalty on which game events are logged
  
  The logger should have the following functionality:
       \begin{enumerate}
          \item \texttt{M-171} Show a timestamp at which the event happend
          \item \texttt{M-172} Show a log priority \citep{apachelog} of the event (\textit{DEBUG}, \textit{INFO}, \textit{WARN}, \textit{ERROR})
          \item \texttt{M-173} Show in which class and at which line number the log is called
          \item \texttt{M-174} Ability to pass objects to a format string \citep{formatstring}. For example: \texttt{log("called on \%s", this)}.
          \item \texttt{M-174} Ability to pass throwables to the log function, which causes
          the Throwables stacktrace to be printed to the outputstream \citep{throwable}
          \item \texttt{M-175} Append log to system outputstream
      \end{enumerate} 
  
  	The following events should be logged:
  
        \begin{enumerate}
          \item \texttt{M-181} When a bubble is shot, along with its direction
          \item \texttt{M-182} When a bubble is popped, along with which type of bubble it is
          \item \texttt{M-183} When a row of bubbles is inserted
          \item \texttt{M-184} When a ammo bubble is created
          \item \texttt{M-185} When points are awarded to the player
          \item \texttt{M-186} When looking for a multiplayer room
          \item \texttt{M-187} When connected to a multiplayer room
          \item \texttt{M-188} When disconnected from a multiplayer room
          \item \texttt{M-189} When an exception is thrown
      \end{enumerate}

% ==========================================
% END M-170: 
% ==========================================

% ==========================================
% ASSIGNMENT 4
% M-190: 20%-time
% ==========================================

\item \texttt{M-190} A player should be able to different choose between game modes

        \begin{enumerate}
          \item \texttt{M-191} \textsc{Classic mode.} No power-up bubbles (see \texttt{M-160})
          \item \texttt{M-192} \textsc{Powerup mode.} Power-up bubbles are loaded into the cannon at a small chance
          \item \texttt{M-193} \textsc{Time mode.} All bubbles should be popped in a certain time
      \end{enumerate}     

% ==========================================
% END M-190: 
% ==========================================


\end{itemize}

% ==========================================
% MOVED THE SHOULD HAVES
% ==========================================
\subsection{Should have}

\begin{itemize}
      \item \texttt{S-130} In singleplayer mode, a player should also have the option to face various levels predefined by a designer
      \item \texttt{S-131} When the player clicks the highscore button he should be able to see a list of highscores
      \item \texttt{S-132} When the game has ended, the score and name of the player should be saved to the highscores
      \item \texttt{S-167} A power-up bubble can have more than one special ability.
\end{itemize}

% ==========================================
% MOVED THE COULD HAVES
% ==========================================
\subsection{Could have}

\begin{itemize}
	\item \texttt{C-150} \textsc{Beginners tutorial.} The controls and the goal of the game are explained when a player selects a button in the menu
      \item \texttt{C-176} Append log to a text file
      \item \texttt{C-193} When a bubble is popped, a pop animation should be played
\end{itemize}

% ==========================================
% ASSIGNMENT 1
% 	NON-FUNCTIONAL REQUIREMENTS
% ==========================================

\section{Non-functional requirements}
\subsection{Product requirements}

\begin{itemize}
  \item \texttt{M-231} The game should be able to run on the desktop computers at the TU Delft
  \item \texttt{M-232} It shouldn't take a user more than five minutes to learn the basics of the game
\end{itemize}

% ==========================================
% ASSIGNMENT 1
% 	ORGANIZATIONAL REQUIREMENTS
% ==========================================

\subsection{Organizational requirements}
This game should be developed using the Java programming language, using the Maven, Git, Devhub tools for Continuous Integration and revision management and JUnit for Test-Driven Development (TDD). Within two weeks a fully functional game should be delivered. We have to work in a team of five.

\subsection{External requirements}
There are no external requirements at this point of the project.

\bibliographystyle{unsrtnat}
\bibliography{bronnen}


\pagebreak


\end{document}
